Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph

### 2021-06-01 sdss-talk/slides-4min.Rmd
updated 4 min presentation slides

@@

## (Generalized) Random Dot Product Graph Model

### Recovery/Estimation

Want to estimate $X$ given $A$.

### Adjacency Spectral Embedding

To embed in $\mathbb{R}^{p+q}$,

1. Compute $A \approx \hat{V} \hat{\Lambda} \hat{V}^\top$ 
where $\hat{\Lambda} \in \mathbb{R}^{(p+q) \times (p+q)}$ and 
$\hat{V} \in \mathbb{R}^{n \times (p+q)}$ by using 
$p$ most positive and $q$ most negative eigenvalues.

2. Let $\hat{X} = \hat{V} |\hat{\Lambda}|^{1/2}$.

\vspace*{.5\baselineskip}

Rubin-Delanchy et al., 2020:  
$$\max_i \|\hat{X}_i - Q_n X_i \| \stackrel{a.s.}{\to} 0$$

$$Q_n \in \mathbb{O}(p, q)$$

>>>>

```{r out.width = '50%', fig.height = 3, fig.width = 4}
Pz <- generate.P.beta(64, 4, 4, 1, 1, 4)
P <- Pz$P
z <- Pz$clustering
A <- draw.graph(P)
qgraph::qgraph(A, groups = factor(z), legend = FALSE)
```

@@
